% !TEX root = ../main.tex

\vspace{-1.0cm} Computational modeling plays a significant role in informing decision-making across many disciplines. For example, economists advise central banks on monetary policy by forecasting the impact of changing interest rates on economic activity. Financial institutions manage their capital requirements by conducting stress tests to evaluate their business viability under adverse market conditions. Epidemiologists guide public mitigation efforts in the current pandemic by
predicting the effect of social distancing rules on the disease's spread.\\

At the same time, decision-making under uncertainty is a significant challenge across scientific domains. Economists struggle to pin down the transmission channels of monetary policy to economic outcomes when deciding on the optimal interest rate. Financial institutions make assumptions about rare events such as financial crises and bank runs when managing their capital requirements. Epidemiologists face substantial uncertainties about the transmission of disease when recommending non-pharmaceutical interventions. All data-driven computational models influencing these decisions are subject to numerous sources of uncertainty. Models are often misspecified, there are numerical approximation errors in the implementation, and their parameterization remains partly uncertain.\\

We embrace the uncertainties involved in model-augmented decision-making. We develop methods and explore applications in science and business that systematically integrate uncertainty in the decision-making process. We use statistical decision theory as a framework to properly analyze model-informed decision-making as a decision problem under uncertainty and structure a well-reasoned and transparent decision process \citep{Blesch.2021, Eisenhauer.2021, Manski.2021}.\\

The application of statistical decision theory is conceptually simple, but computationally challenging. This note offers a brief overview of statistical decision theory, points to its computational challenges, and concludes with an application example.\newpage
